Using CopyKAT to identify tumor cells in Ewing sarcoma samples

### 2024-06-17 analyses/cell-type-ewings/template_notebooks/03-copykat.Rmd
Revert "Merge branch 'main' into sjspielman/517-module-gha"
This reverts commit b5e9160f58f517604d962dfc92b2606416e3c49b, reversing
changes made to 1f4cd82978d8ca81c36cf5fd3a97ea4b60792526.

all_info_df <- cnv_df |> 
  dplyr::select(barcodes,
                mean_cnv_detection) |> 
  dplyr::group_by(barcodes) |>
  dplyr::mutate(mean_cnv_detection = mean(mean_cnv_detection)) |> 
  dplyr::distinct() |> 
  dplyr::left_join(celltype_df)

readr::write_tsv(all_info_df, copykat_results_file)
```

>>>>

readr::write_tsv(celltype_df, copykat_results_file)
```
